[dcpo_demsupport]

### 2020-08-02 paper/dcpo_demsupport.Rmd
clean up

load(here::here("data", "dcpo_input_update.rda"))
load(here::here("data", "dcpo_theta.rda"))

df_controls <- read_csv(here::here("data", "control_variables.csv"),
                        col_types = cols(.default = col_double(),
                                         country = col_character(),
                                         country_name = col_character(),
                                         ISO = col_character(),
                                         Region_UN = col_character(),
                                         Region_UN.1 = col_character())) %>% 
  mutate(country0 = iconv(country, "latin1", "UTF-8", sub=''),
         country = countrycode::countrycode(country0, "country.name", "country.name"))

@@

result_dcpo_1k <- map(df_theta, function(aDataset) {
  plm(
    Vdem_libdem ~ plm::lag(Vdem_libdem, 1:2) + plm::lag(theta, 1) + plm::lag(lg_imp_mdpgdp, 1) + plm::lag(mdprgdp_grwth, 1) + plm::lag(Region_UN, 1) + plm::lag(muslism_prop_2010, 1) + plm::lag(dependence_pc_di, 1),
    model = "pooling",
    data = aDataset
  )
})

>>>>

# load(here::here("data", "dcpo_input_update.rda"))
load(here::here("data", "dcpo_theta.rda"))

df_controls <- read_csv(here::here("data", "control_variables.csv"),
                        col_types = cols(.default = col_double(),
                                         country = col_character(),
                                         country_name = col_character(),
                                         ISO = col_character(),
                                         Region_UN = col_character())) %>% 
  mutate(country0 = iconv(country, "latin1", "UTF-8", sub=''),
         country = countrycode::countrycode(country0, "country.name", "country.name"))

@@

result_dcpo_1k <- map(df_theta, function(aDataset) {
  plm(Vdem_libdem ~ plm::lag(Vdem_libdem, 1:2) + plm::lag(theta, 1) +
        plm::lag(lg_imp_mdpgdp, 1) + plm::lag(mdprgdp_grwth, 1) +
        plm::lag(Region_UN, 1) + plm::lag(muslism_prop_2010, 1) +
        plm::lag(dependence_pc_di, 1),
    model = "pooling",
    data = aDataset
  )
})
